%-------------------------
% Resume in LateX
% Author : Sidati NOUHI
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}


% Custom
% \usepackage{fontspec}
%
% % Set the main body font
% \setmainfont{Inter} 
%
% % Set a monospaced font for your GitHub link or tech stack
% \setmonofont{Source Code Pro}

% \begin{document}
%     {\LARGE \textbf{Jane Doe}} \\
%     \texttt{github.com/janedoe} % Monospaced look for links
%
%     \section*{Technical Skills}
%     \textbf{Languages:} Java, Python, C++, Go
% \end{document}


% Just in case someone needs a heading that does not need to be in a list
% \usepackage{helvet}
% \renewcommand{\familydefault}{\sfdefault}

\setlength{\footskip}{5pt}

\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\textbf{\Huge Sidati NOUHI} \\[0.2cm]
\small{\textbf{Email:} \href{mailto:sidatinouhi@gmail.com}{sidatinouhi@gmail.com} \quad
\textbf{Mobile:} \href{tel:+212655425113}{+212 655425113}} \\[0.1cm]
\small{\textbf{GitHub:} \href{https://github.com/sidatii}{github.com/sidatii} \quad
\textbf{LinkedIn:} \href{https://linkedin.com/in/yourprofile}{linkedin.com/in/sidati.nouhi}}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {UM6P - YouCode school}{Safi, Maroc}
      {Software developement}{Sep 2022 -- Juil 2024}
    \resumeSubheading
      {Universite Ibn zohr}{Agadir, Maroc}
      {Master -- ingenierie financiere et modelisation}{Sep 2019 -- Juil 2021}
    \resumeSubheading
      {Universite Ibn zohr}{Agadir, Maroc}
      {License -- Economie \& Modelisation}{Sep 2016 -- July 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {Eurafric Information}{Casablanca, Morocco}
      {Full stack developer}{Mar 2024 -- Present}
      \resumeItemListStart
      \resumeItem{Backend Development}
      {Designed and implemented RESTful APIs using Spring Boot, JPA, and Spring Security for secure data access and business logic implementation.}
      \resumeItem{Frontend Development}
      {Developed responsive user interfaces using Angular framework with TypeScript, implementing modern UI/UX patterns and component-based architecture.}
      \resumeItem{Database Management}
      {Managed OracleDB databases, optimized queries, and implemented data caching strategies using Redis for improved application performance.}
      \resumeItem{System Integration}
      {Integrated biometric data processing systems including OCR, face matching, and face detection capabilities for enhanced security features.}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
  %  \resumeSubSubheading
  %   {Software Engineer I}{Oct 2014 -- Sep 2016}
  %   \resumeItemListStart
  %      \resumeItem{Apache Beam}
  %        {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
  %   \resumeItemListEnd

%-------------------------------------------

    \resumeSubheading
      {AgriIn - Platform de gestion des audits agricoles}{Remote, CA}
      {Backend Developer}{Jan 2014 -- Oct 2016}
      \resumeItemListStart
        \resumeItem{Product Design}
        {Designed scalable backend architecture and APIs for agricultural audit management platform, ensuring high performance and maintainability for enterprise clients.}
        \resumeItem{Database Schema Design}
        {Developed comprehensive database schemas for complex agricultural data models, implementing efficient indexing strategies and data relationships for optimal query performance.}
        \resumeItem{Caching Implementation}
        {Implemented advanced caching strategies using Redis and in-memory solutions to reduce database load and improve application response times by 60\%.}
        \resumeItem{Security Architecture}
        {Built robust security frameworks including authentication, authorization, and data encryption to protect sensitive agricultural and financial data.}
        \resumeItem{Payment Processing}
        {Integrated multiple payment gateways and implemented secure transaction processing systems handling various payment methods and currencies.}
        \resumeItem{Multitenancy Architecture}
        {Designed and implemented multitenant database architecture supporting multiple clients with isolated data while maintaining efficient resource utilization.}
      \resumeItemListEnd

    \resumeSubheading
      {Lucena Research}{Atlanta, GA}
      {Data Scientist}{Summer 2012 and 2013}
      \resumeItemListStart
        \resumeItem{Portfolio Management}
          {Created models for portfolio hedging, portfolio optimization and price forecasting. Also created a strategy backtesting engine used for simulating and backtesting strategies.}
        \resumeItem{QuantDesk}
          {Python backend for a web application used by hedge fund managers for portfolio management.}
      \resumeItemListEnd

    \resumeSubheading
      {Cegedim R\&D}{[Location]}
      {R\&D Intern}{[Date Range]}
      \resumeItemListStart
        \resumeItem{CI/CD Pipeline Optimization}
        {Optimized CI/CD pipelines for improved deployment efficiency, reducing build times by 40\% and increasing deployment frequency through automated testing and parallel processing.}
        \resumeItem{Automation Implementation}
        {Implemented automated testing frameworks and deployment scripts, streamlining the software delivery process and reducing manual intervention by 70\%.}
        \resumeItem{Performance Monitoring}
        {Developed monitoring solutions for CI/CD pipeline performance, implementing metrics collection and alerting systems for proactive issue detection.}
        \resumeItem{Infrastructure as Code}
        {Worked on Infrastructure as Code practices using configuration management tools to ensure consistent and reproducible deployment environments.}
      \resumeItemListEnd

   \resumeSubHeadingListEnd


%-----------TECHNOLOGIES-----------------
\section{Technologies}

\textbf{Backend:} Java, Spring Boot, Spring Framework (JPA, Security), REST APIs, Microservices, Redis \\
\textbf{Frontend:} Angular, TypeScript, JavaScript, HTML5, CSS3 \\
\textbf{Database:} OracleDB, MySQL, PostgreSQL, MongoDB \\
\textbf{CI/CD:} Docker, Kubernetes, Jenkins, GitLab CI, GitHub Actions


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\textbf{BIAN Party Management System (KYC)} \textbf{[IN PROGRESS]}}
      {A BIAN compliant microservices-based system for managing parties, using Spring Framework (Spring Boot, JPA, Security, batch, springdocs, Neo4j), Redis, and OracleDB.}
    \resumeSubItem{Correspondent Banking (FKYC)}
      {Built a comprehensive correspondent banking management system (FKYC) using Spring Framework (Spring Boot, JPA, Security), Redis, OracleDB, and Angular for the frontend.}
    \resumeSubItem{Biometric Data Processing System}
      {Implemented OCR, face matching, and face detection capabilities for biometric data processing using Spring Framework (Spring Boot, JPA, Security), Redis, OracleDB, and Angular.}
    \resumeSubItem{Agri In platform}
    {comprehensive agricultural audit management platform with scalable backend architecture and multitenant database design.}
    \resumeSubItem{\textbf{Genc} \textbf{[IN PROGRESS]}}
    {An open-source build system for C/C++ projects, built using C, designed to build, test and manage dependencies efficiently.}
    \resumeSubItem{Xpscan}
    {An open-source TCP port scanner built in C++, capable of scanning large IP ranges efficiently using multithreading and raw socket programming.}
  \resumeSubHeadingListEnd

%
%--------SKILLS------------
%\section{Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, JavaScript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
